Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-01-08 article.tex
Change to a4paper
Add affiliations

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

@@

\title{Poincaré and SimBio: a versatile and extensible Python ecosystem
for modeling systems.}
\author{Mauro Silberberg \and Rahuman S. Malik-Sheriff \and Henning
Hermjakob \and Hernán E. Grecco}
\date{}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  a4paper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

@@

\usepackage{authblk}

\title{Poincaré and SimBio: a versatile and extensible Python ecosystem
for modeling systems.}
\author[1,2]{Mauro Silberberg}
\author[3]{Rahuman S. Malik-Sheriff}
\author[3]{Henning Hermjakob}
\author[1,2]{Hernán E. Grecco}
\affil[1]{Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Física. Buenos Aires, Argentina.}
\affil[2]{CONICET - Universidad de Buenos Aires, Instituto de Física de Buenos Aires (IFIBA). Buenos Aires, Argentina}
\affil[3]{European Bioinformatics Institute, European Molecular Biology Laboratory (EMBL-EBI), Wellcome Trust Genome Campus, Cambridge, UK}
\date{}
